\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
fix capitalization

 \noindent \emph{Deep Learning:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. %This family of work is closest to our RF/DC baseline.
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 Our work  considers a weakly-supervised regime where ground truth programs are not provided and
 the agent must learn from a few hundred tasks.

>>>>

 \noindent \emph{Deep learning:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. %This family of work is closest to our RF/DC baseline.
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 Our work  considers a weakly-supervised regime where ground truth programs are not provided and
 the agent must learn from a few hundred tasks.
